High-order dynamic neural correlations reflect naturalistic processing in humans

### 2019-05-09 paper/main.tex
L draft done

We applied timecorr, using delta and gaussian kernels
Fig.~\ref{fig:weights}) to each of these 
synthetic datasets, then correlated each recovered
correlation matrix with the ground truth.  We repeated this process 10
times and explored how recovery varies
with the kernel and the specific structure of the data. For the
ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  C.)  and for the
block synthetic dataset (Fig.~\ref{fig:synthetic_data},  D.)  we made further
comparisons of the timecorr recovered correlation matrices. We
compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
C.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
the block specific covariance matrix (Block 1-5,
Fig.~\ref{fig:synthetic_data},  D.).

@@

We found that, during each of the listening conditions in the
experiment, classifiers that incorporated second-order correlations
yielded consistently higher accuracy than classifiers trained only on
lower-order patterns (Fig.~\ref{fig:decoding_level},  A.).  (Incorporating higher-order correlations did
not further improve decoding accuracy.)  By contrast, these
higher-order correlations were not necessary to support (minimally
above chance) decoding during a control rest condition.  This suggests
that the cognitive processing that supported the listening conditions
involved second-order (or higher) network dynamics.

@@

How can we better understand how these brain patterns changing over
time? How to quantify the potential network dynamics that we might be
driving these changes? One way to judge the techniques of the future is
to look at the trajectory of the fMRI field so far has taken so far
(Fig.~\ref{fig:methods_fig}).  The field started with 
univariate activation, measuring the average activity for each voxel.
Analyses of multivariate activation followed, looking at spatial patterns of
activity over voxels. Next, correlations of activity were explored, first
with measures like resting connectivity that take temporal correlation
between a seed voxel and all other voxels then with full connectivty
that measure all pairwise correlations.  Additionally, this path of increasing
complexity also moved from static to dynamic measurements.  One
logical next step in this trajectory would be dynamic higher-order
correlations. We have created a method 
to support these calculations.

>>>>

We applied timecorr, using delta and gaussian (width = 10) kernels
Fig.~\ref{fig:weights}) to each of these 
synthetic datasets, then correlated each recovered
correlation matrix with the ground truth.  We repeated this process 10
times and explored how recovery varies
with the kernel and the specific structure of the data. For the
ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  C.)  and for the
block synthetic dataset (Fig.~\ref{fig:synthetic_data},  D.)  we made further
comparisons of the timecorr recovered correlation matrices. We
compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
C.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
the block specific covariance matrix (Block 1-5,
Fig.~\ref{fig:synthetic_data},  D.).

@@

We found that, during each of the listening conditions in the
experiment, classifiers that incorporated second-order correlations
yielded consistently higher accuracy than classifiers trained only on
lower-order patterns (Fig.~\ref{fig:decoding_level},  A.), and incorporating higher-order correlations did
not further improve decoding accuracy.  By contrast, these
higher-order correlations were not necessary to support (minimally
above chance) decoding during a control rest condition.  This suggests
that the cognitive processing that supported the listening conditions
involved second-order (or higher) network dynamics.

@@

How can we better understand how brain patterns change over
time? How can we quantify the potential network dynamics that might be
driving these changes? One way to judge the techniques of the future is
to look at the trajectory of the fMRI field so far has taken so far
(Fig.~\ref{fig:methods_fig}).  The field started with 
univariate activation, measuring the average activity for each voxel.
Analyses of multivariate activation followed, looking at spatial patterns of
activity over voxels. Next, correlations of activity were explored, first
with measures like resting connectivity that take temporal correlation
between a seed voxel and all other voxels then with full connectivty
that measure all pairwise correlations.  Additionally, this path of increasing
complexity also moved from static to dynamic measurements.  One
logical next step in this trajectory would be dynamic higher-order
correlations. We have created a method 
to support these calculations by scalably approximating dynamic higher-order
correlations.
